\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 lang-design.tex
use "computational behaviors" in lang-design.tex

A key observation is that although late binding
prevents \emph{definitional equality} on \lsti{subst}, it does not
affect \emph{propositional equality}.
That is, \lsti{\forall x t, subst tm_unit x t = tm_unit},
as a proposition (\lsti{Prop}), should still hold.
After all, how \lsti{subst} is defined on \lsti{tm_unit} does not vary
from a base family to a derived family.
%\EDJ{I think the reviewer might ask : what if the subst late-bound tm_unit case/why the subst cases cannot be late-bound? it not necessary return tm_unit in those case. 
%\\ What the plugin generates is actually subst tm_unit x t = subst.tm_unit. In other words, it points back to the handler instead of the concrete constructor. That is one of the advantage of looking FRecursion as a family.}\YZreply{Currently the paper is taking the position that case handlers cannot be further bound, to make the story simpler.}
What varies is \lsti{subst} itself as a recursive function combining the case handlers.
%
Based on this insight, \Lang automatically generates
a propositional equality for each case handler defined within \lsti{FRecursion},
making the equalities and the recursive function available as axioms for use by the rest of the current family.
\Lang also provides a tactic \lsti{fsimpl} that enables, for instance,
simplifying \lsti{subst tm_unit x t'} to \lsti{tm_unit}.
Under the hood, \lsti{fsimpl} works by rewriting applications of the
axiomatized recursive function using the axiomatized propositional equalities.

@@

\noindent
As expected, "tm_prect_STLC" is axiomatized along with
four (propositional) equalities, one for each constructor of "tm".
For instance, the equality for constructor "tm_abs" is as follows:

@@

\noindent
and then rewrites the above equality using two of the axiomatized
equalities about "tm_prect_STLC",
%(namely "tm_var_eq_STLC" and "tm_abs_eq_STLC"),
obtaining \lsti{Some 1 = Some 3},
from which \lsti{False} easily follows.

Note that the proof term generated by \lsti{fdiscriminate H} in "STLC"
is reusable by family "STLCFix", because the partial recursor and its
equalities are compatible with the late binding of "tm".
Also note that within family "STLCFix", a second partial recursor
(called "tm_prect_STLCFix") and its equalities are available,
allowing \lsti{tm_fix} properties such as \lsti[basicstyle=\fontsize{8.5}{9}]{tm_fix x t1 = tm_fix x t2 -> t1 = t2} to be proved.

>>>>

A key observation is that although late binding
prevents \emph{definitional equality} on \lsti{subst}, it does not
affect \emph{propositional equality}.
That is, \lsti{\forall x t, subst tm_unit x t = tm_unit},
as a proposition (\lsti{Prop}) about the computational behavior of \lsti{subst},
should still hold.
After all, how \lsti{subst} is defined on \lsti{tm_unit} does not vary
from a base family to a derived family;
%\EDJ{I think the reviewer might ask : what if the subst late-bound tm_unit case/why the subst cases cannot be late-bound? it not necessary return tm_unit in those case. 
%\\ What the plugin generates is actually subst tm_unit x t = subst.tm_unit. In other words, it points back to the handler instead of the concrete constructor. That is one of the advantage of looking FRecursion as a family.}\YZreply{Currently the paper is taking the position that case handlers cannot be further bound, to make the story simpler.}
what can vary is \lsti{subst} itself as a recursive function combining the case handlers.

Based on this insight, \Lang automatically generates
a propositional equality for each case handler defined within \lsti{FRecursion},
making the equalities and the recursive function available as axioms for use by the rest of the current family.
\Lang also provides a tactic \lsti{fsimpl} that enables, for instance,
simplifying \lsti{subst tm_unit x t'} to \lsti{tm_unit}.
\lsti{fsimpl} works by rewriting applications of the
axiomatized recursive function using the axiomatized equalities about its computational behaviors.

@@

\noindent
As expected, "tm_prect_STLC" is axiomatized along with
four equalities describing its computational behaviors, one for each constructor.
For instance, the equality for constructor "tm_abs" is as follows:

@@

\noindent
and then rewrites the above equality using the axiomatized computational behaviors
of "tm_prect_STLC",
%(namely "tm_var_eq_STLC" and "tm_abs_eq_STLC"),
obtaining \lsti{Some 1 = Some 3},
from which \lsti{False} easily follows.
%
Note that the proof term generated by \lsti{fdiscriminate H} in "STLC"
is reusable by family "STLCFix", because the partial recursor and its
computational behaviors are compatible with the late binding of "tm".

Within family "STLCFix", a second partial recursor
(called "tm_prect_STLCFix") and its computational behaviors are axiomatized,
so properties such as \lsti[basicstyle=\fontsize{8.25}{9},columns=fixed,basewidth=0.9ex]{tm_fix x t1 = tm_fix x t2 ->  t1 = t2} can be proved.
